Bayesian Shape Reconstruction and Optimal Guidance for Autonomous Landing on Asteroids

### 2020-07-17 manuscript.tex
JAS submission 0

\documentclass[journal]{new-aiaa}
%\documentclass[conf]{new-aiaa} for conference papers
\usepackage{AAS_packages}
% \usepackage[utf8]{inputenc}

@@

% TODO Think about adding current affiliation as a note, need to ask company
\author{Shankar Kulumani \footnote{PhD, Mechanical and Aerospace Engineering, \href{mailto:skulumani@gwu.edu}{skulumani@gwu.edu}}
and
Taeyoung Lee \footnote{Associate Professor, Mechanical and Aerospace Engineering, \href{mailto:tylee@gwu.edu}{tylee@gwu.edu}}}
\affil{The George Washington University, Washington, DC, 20052}

@@

\begin{abstract}
    Constructing of the precise shape of an asteroid is critical for spacecraft operations, as the gravitational potential is determined by spatial mass distribution.
    For example, the standard method of determining the gravitational potential of an asteroid, through the use of a polyhedron potential model, is directly dependent on the shape model.
    Furthermore, safe landing or close-proximity operations requires accurate knowledge of the surface topology. 
    The typical approach to shape determination requires a prolonged ``mapping'' phase of the mission over which extensive measurements are collected and transmitted for Earth-based processing.
    This paper presents a set of approaches to explore an unknown asteroid with onboard calculations, and to land on its surface area selected in an optimal fashion. 
    The main motivation is to avoid the extended period of mapping phase or preliminary ground observations that are commonly required in spacecraft mission around asteroids. 
    First, range measurements from spacecraft to the surface are used to incrementally correct an initial shape estimate according to the Bayesian framework. 
    Then, an optimal guidance scheme is proposed to control the vantage point of the range sensor to construct a complete 3D model of the asteroid shape. 
    This shape model is then used in a nonlinear controller to track a desired trajectory about the asteroid.
    Finally, a multi resolution approach is presented to construct a higher fidelity shape representation in a specified location while avoiding the inherent burdens of a uniformly high resolution mesh. 
    This approach enables for an accurate shape determination around a potential landing site.
    We demonstrate this approach using several radar shape models of asteroids and provide a full dynamic simulation about asteroid 4769 Castalia.
\end{abstract}

@@

Another key dynamic consideration is the coupling between rotational and translational states around the asteroid.
The coupling is induced due to the different gravitational forces experienced on various portions of the spacecraft. 
The effect of the gravitational coupling is related to the ratio of the spacecraft size and orbital radius~\cite{hughes2004}.
For operations around asteroids, the ratio is relatively large which causes a much larger coupling between the translational and rotational states.
\citeauthor{elmasri2005}~\cite{elmasri2005} and \citeauthor{sanyal2004a}~\cite{sanyal2004a} investigated the coupling of an elastic dumbbell spacecraft in orbit about a central body, but only considered the case of a spherically symmetric central body.
Furthermore, the spacecraft model is assumed to remain in a planar orbit.
As a result, these developments are not directly applicable to motion about an asteroid, which experiences highly non-Keplerian motion.
\citeauthor{misra2015b}~\cite{misra2015b} investigated the effect of coupled motion on long term trajectories around asteroids.
However, the analysis only considered a second order spherical harmonic gravitational potential model. 
Therefore, these results are only valid when far from the asteroid surface and will diverge when used within the Brillouin sphere.

@@

Mixed resolution surface meshes are routinely used in finite element and geometric modeling applications~\cite{botsch2010}.
As shown in Reference~\citenum{mcmahon2017}, utilizing mixed resolution shape models for asteroid missions offers the potential of reduced computational demands.
The computational cost of the polyhedron potential model, given by~\cref{eq:attraction}, is roughly proportional to the number of faces in the shape model.
As a result, a uniformly high resolution shape would quickly become intractable for real time operations.
However, utilizing a mixed resolution approach allows for a high fidelity in a smaller mission critical area, such as a landing site, with a limited impact on the computational cost.

@@

\section{Acknowledgement}
This research is supported in part by NSF under the grant CMMI-1335008.

\bibliography{library}

>>>>

%% The following three lines were added to by pass an error
%% See https://tex.stackexchange.com/questions/108394/tex-capacity-exceeded-sorry-input-stacksize-5000
\makeatletter
\def\cl@chapter{}
\makeatother
%%
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
\usepackage{AAS_packages}
%\usepackage[numbers]{natbib}
% \usepackage[utf8]{inputenc}

@@

\author{Shankar Kulumani         \and
        Taeyoung Lee %etc.
}

%\authorrunning{Short form of author list} % if too long for running head

% todo: we may update the affiliation and the address of Shankar 
\institute{S. Kulumani (corresponding author) \at
              Mechanical and Aerospace Engineering, The George Washington University, Washington DC, 20052\\
              \email{shanks.k@gmail.com}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           T. Lee,  \at
              Mechanical and Aerospace Engineering, The George Washington University, Washington DC, 20052\\
              \email{tylee@gwu.edu}
}

@@

\begin{abstract}
    Constructing of the precise shape of an asteroid is critical for spacecraft operations, as the gravitational potential is determined by spatial mass distribution.
    %For example, the standard method of determining the gravitational potential of an asteroid, through the use of a polyhedron potential model, is directly dependent on the shape model.
    %Furthermore, safe landing or close-proximity operations requires accurate knowledge of the surface topology. 
    The typical approach to shape determination requires a prolonged ``mapping'' phase of the mission over which extensive measurements are collected and transmitted for Earth-based processing.
    This paper presents a set of approaches to explore an unknown asteroid with onboard calculations, and to land on its surface area selected in an optimal fashion. 
    The main motivation is to avoid the extended period of mapping phase or preliminary ground observations that are commonly required in spacecraft mission around asteroids. 
    First, range measurements from spacecraft to the surface are used to incrementally correct an initial shape estimate according to the Bayesian framework. 
    Then, an optimal guidance scheme is proposed to control the vantage point of the range sensor to construct a complete 3D model of the asteroid shape. 
    This shape model is then used in a nonlinear controller to track a desired trajectory about the asteroid.
    Finally, a multi resolution approach is presented to construct a higher fidelity shape representation in a specified location while avoiding the inherent burdens of a uniformly high resolution mesh. 
    This approach enables for an accurate shape determination around a potential landing site.
    We demonstrate this approach using several radar shape models of asteroids and provide a full dynamic simulation about asteroid 4769 Castalia.
    \keywords{Asteroids \and Shape Construction \and Guidance \and Optimization}
\end{abstract}

@@

Another key dynamic consideration is the coupling between rotational and translational states around the asteroid.
The coupling is induced due to the different gravitational forces experienced on various portions of the spacecraft. 
The effect of the gravitational coupling is related to the ratio of the spacecraft size and orbital radius~\cite{hughes2004}.
For operations around asteroids, the ratio is relatively large which causes a much larger coupling between the translational and rotational states.
In~\cite{elmasri2005} and \cite{sanyal2004a}, the coupling of an elastic dumbbell spacecraft in orbit about a central body is considered, assuming that the central body is spherically symmetric.
Furthermore, the spacecraft model is assumed to remain in a planar orbit.
As a result, these developments are not directly applicable to motion about an asteroid, which experiences highly non-Keplerian motion.
In~\cite{misra2015b}, the effect of coupled motion is investigated for long term trajectories around asteroids.
However, the analysis only considered a second order spherical harmonic gravitational potential model. 
Therefore, these results are only valid when far from the asteroid surface and will diverge when used within the Brillouin sphere.

@@

Mixed resolution surface meshes are routinely used in finite element and geometric modeling applications~\cite{botsch2010}.
As shown in Reference~\cite{mcmahon2017}, utilizing mixed resolution shape models for asteroid missions offers the potential of reduced computational demands.
The computational cost of the polyhedron potential model, given by~\cref{eq:attraction}, is roughly proportional to the number of faces in the shape model.
As a result, a uniformly high resolution shape would quickly become intractable for real time operations.
However, utilizing a mixed resolution approach allows for a high fidelity in a smaller mission critical area, such as a landing site, with a limited impact on the computational cost.

@@

%\section{Acknowledgement}
%This research is supported in part by NSF under the grant CMMI-1335008.

\bibliographystyle{IEEEtran}
\bibliography{library}
